### 2023-11-21 chapters/introduction.tex
Update description of Corti

\section{Uncertainty by example: Corti use-cases}
%
% OUTLINE: Motivate the research project. 
% - What is the context of the research and why is it important? 
% - What are the current applications of machine learning in the domain (decision-support in healthcare)?
% - What are the practical implications of the research? 
% - What are the challenges and limitations of the current state-of-the-art?
%
At the start of this project in 2020, Corti's main product was a software system providing decision-support for call-takers that operate the 1-1-2 emergency line in Copenhagen, Denmark, and the 9-1-1 emergency line in Seattle, Washington, in the United States.
The system is in continued use in 2023, and provides an interface for navigating a graph-based protocol, defined by the local emergency medical services, which call-takers use to triage patients during emergency calls. 
Calls are transcribed in real-time using automatic speech recognition built for the customer-domain and the system makes suggestions for the call-taker to use in the conversation with the caller, including notifications about forgotten protocol questions \parencite{havtorn_multiqt_2020} and potential cases of cardiac arrests \parencite{cite15, cite14}. The system logs the details about the call and the actions taken by the call-taker for later use in review, training and quality assurance.

\moretodo[inline]{Update description of Corti. Focus on the current year. }

>>>>

\section{Uncertainty by example: Corti use-cases}
%
% OUTLINE: Motivate the research project. 
% - What is the context of the research and why is it important? 
% - What are the current applications of machine learning in the domain (decision-support in healthcare)?
% - What are the practical implications of the research? 
% - What are the challenges and limitations of the current state-of-the-art?
%
Corti develops decision support software for healthcare professionals such as general practitioners, medical coders, and call-takers at emergency medical services. The system supports the professional similar to a copilot for medical interviews, for instance providing a graph-based protocol for triaging and helping to keep track of key information shared in the conversation.

When used by emergency services for example, calls are transcribed in real-time using automatic speech recognition built for the customer-domain and the system makes suggestions for the call-taker to use in the conversation with the caller, including notifications about forgotten protocol questions \parencite{havtorn_multiqt_2020} and potential cases of cardiac arrests \parencite{cite15, cite14}. The system logs the details about the call and the actions taken by the call-taker for later use in review, training and quality assurance.
